\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{booktabs}
\usepackage{hyperref}
\fontfamily{garamond}
\selectfont

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan
}

\urlstyle{same}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.8in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}

%-----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1}}\end{minipage}}}}

%-----------------------------------------------------------
\begin{document}

\hspace{0.5cm}\\[-1.8cm]

\textbf{VIRINCHI ADDANKI} \hspace{8.0cm} {\bf \href{mailto:virinchiaddanki@gmail.com}{virinchiaddanki@gmail.com}}\\
\indent {\bf Automation Engineer | Python} \hspace{6.7cm} {\bf +91 6300906085} \\
\indent {\bf Hyderabad, India} \hspace{8.9cm}
{\bf \href{https://www.linkedin.com/in/virinchi-addanki/}{LinkedIn} | \href{https://github.com/addanki-virinchi}{GitHub} | \href{https://virinchi-addanki.onrender.com/}{Portfolio}}\\

\vspace{-2mm}

%-----------------------------------------------------------
\resheading{\textbf{PROFESSIONAL SUMMARY}}\\[\lsep]\\

\hspace{0.11cm}
\begin{minipage}{0.98\textwidth}
Python Automation Engineer with 1+ year of production experience building
\textbf{workflow automation systems, browser-based automation, and cloud-deployed
scheduled tasks}.
Proven track record of deploying automation on \textbf{Google Cloud Platform}
(Compute Engine, GKE) and handling complex, JavaScript-driven applications using
\textbf{Selenium and Playwright}.
Experienced in building full-stack automation platforms with
\textbf{REST APIs, JWT authentication, Firebase, and third-party integrations},
reducing manual workloads by up to \textbf{90\%} and ensuring reliable,
time-bound execution.
\end{minipage}

\vspace{4mm}

%-----------------------------------------------------------
\resheading{\textbf{PROFESSIONAL EXPERIENCE}}

\begin{itemize}

\item {\bf Software Engineer — Automation \& Cloud Infrastructure}
\textit{[BotRecruit]}
\textit{\hfill {Jan 2025 -- Jan 2026 | UK (Remote)}}
\begin{itemize}
\item Architected and deployed production-grade automation workflows
to optimize operational scheduling on dynamic, JavaScript-rendered platforms.
\item Designed resilient browser automation using
\textbf{Selenium and Playwright} with robust session handling and wait strategies.
\item Containerized and deployed automation services on
\textbf{Google Kubernetes Engine and Compute Engine}
to enable scalable, infrastructure-independent execution.
\item Configured \textbf{Cron Jobs and instance scheduling}
to trigger automation within defined operational windows,
maintaining consistent on-time execution across time zones.
\item Built automated validation and monitoring checks that reduced
operational errors by over \textbf{90\%}.
\item Implemented CI/CD pipelines using \textbf{GitHub Actions}
for automated testing and deployment.
\end{itemize}

\end{itemize}

\begin{itemize}

\item {\bf Python Engineer (Freelance) — Full-Stack Automation}
\textit{[CRM Group Consulting]}
\textit{\hfill {Sep 2024 -- Feb 2025 | US (Remote)}}
\begin{itemize}
\item Built \textbf{VocalLocal}, an AI-powered platform for recording,
transcribing, and translating audio across \textbf{20+ languages}.
\item Engineered backend services using \textbf{Django and FastAPI},
exposing secure REST APIs consumed by a web frontend.
\item Implemented \textbf{JWT-based authentication}
and controlled access for user sessions and third-party services.
\item Integrated \textbf{Firebase (Firestore)} for real-time data storage
and session metadata management.
\item Automated AI workflows using third-party language models,
reducing communication delays by up to \textbf{80\%}.
\item Implemented subscription-based billing and automated payment workflows.
\end{itemize}

\end{itemize}

\begin{itemize}

\item {\bf Freelance Python \& Automation Engineer}
\textit{[Independent Consultant]}
\textit{\hfill {Sep 2024 -- Present | Remote}}
\begin{itemize}
\item Built scalable automation and data collection pipelines
for international clients across multiple business domains.
\item Integrated authenticated and custom data interfaces
to extract structured datasets from complex platforms.
\item Developed a \textbf{React + Firebase} platform with
JWT-based authentication for automated data ingestion and storage.
\item Automated targeted lead data collection for a consumer-facing startup,
increasing outreach effectiveness by \textbf{80\%}.
\item Processed and standardized \textbf{400,000+ records}
using Pandas-based cleaning, normalization, and deduplication logic.
\end{itemize}

\end{itemize}

%-----------------------------------------------------------
\resheading{\textbf{INTERNSHIPS}}

\begin{itemize}

\item {\bf Web Scraping Intern} \textit{[JustGetLeads]}
\textit{\hfill {Oct 2024 -- Dec 2024 | Remote}}
\begin{itemize}
\item Automated collection and structuring of restaurant and catering
business datasets to support scalable client outreach.
\end{itemize}

\item {\bf Data Scraper Intern} \textit{[1.5 Degree]}
\textit{\hfill {Feb 2025 -- Apr 2025 | Remote}}
\begin{itemize}
\item Automated repetitive business research workflows and
structured datasets for internal analytics and reporting.
\end{itemize}

\end{itemize}

%-----------------------------------------------------------
\resheading{\textbf{KEY PROJECTS}}

\begin{itemize}

\item {\bf VocalLocal — AI Automation Platform}
\begin{itemize}
\item End-to-end automation of AI-driven transcription and translation
using Django, FastAPI, Firebase, JWT, and subscription billing.
\item Actively serving real users in a production environment.
\end{itemize}
\item{\bf Intelligent PDF Data Extraction using Qwen-32B LLM}
\begin{itemize}
    \item Integrated the Qwen-32B model from Hugging Face into a local pipeline to perform context-aware extraction of structured data from complex and unstructured PDF documents.
    \item Automated preprocessing, OCR handling, and JSON-based output generation to enable scalable batch processing and downstream analytics.
\end{itemize}

\item {\bf Nationwide School Data Extraction System (India)}
\begin{itemize}
\item Developed scalable, multithreaded scraping scripts to extract and structure data for 4,00,000+ schools across India.
\item Implemented logging, retry mechanisms, and robust error handling to ensure reliable large-scale data collection and processing.
\end{itemize}

\item {\bf Internal Data Platform (In Progress)}
\begin{itemize}
\item Developing a React + Firebase platform with authenticated
REST endpoints for automated data ingestion and retrieval.
\end{itemize}

\end{itemize}

%-----------------------------------------------------------
\resheading{\textbf{TECHNICAL SKILLS}}

\begin{itemize}
\item \textbf{Languages:} Python, JavaScript, SQL
\item \textbf{Automation:} Selenium, Playwright, BeautifulSoup
\item \textbf{APIs \& Auth:} REST APIs, FastAPI, JWT, Third-Party API Integrations
\item \textbf{Cloud \& DevOps:} GCP (Compute Engine, GKE), Docker, Cron Jobs, GitHub Actions
\item \textbf{Web / Full-Stack:} Django, React (JSX), Firebase (Firestore), HTML, CSS
\item \textbf{Data:} Pandas, NumPy, MySQL, MongoDB, Data Cleaning, JSON Normalization
\item \textbf{Tools:} Postman, VS Code, Jupyter, Git, Claude Code, Cursor, Overleaf
\end{itemize}

%-----------------------------------------------------------
\resheading{\textbf{EDUCATION}}\\[\lsep]\\

\indent
\begin{tabular}{ p{3cm} @{\hskip 0.15in} p{6cm} @{\hskip 0.15in} p{4cm} @{\hskip 0.15in} p{2cm} }
\toprule
\textbf{Degree} & \textbf{Institute} & \textbf{Year} & \textbf{Score} \\
\midrule
B.Tech (CSE) & Parul University, Gujarat & 2021--2025 & 8.19 CGPA \\
Senior Secondary & Narayana Junior College, Vijayawada & 2019--2021 & 94.8\% \\
High School & St. John's, Bantumilli & 2019 & 10 CGPA \\
\bottomrule
\end{tabular}



\vspace{3mm}

%-----------------------------------------------------------
\resheading{\textbf{CERTIFICATIONS}}

\begin{itemize}
\item SQL Bootcamp -- Udemy \\
\href{https://www.udemy.com/certificate/UC-d3b76d22-69b1-45dc-86fd-7a969b920a5e/}{Certificate Link}

\item SQL (Intermediate) -- HackerRank \\
\href{https://www.hackerrank.com/certificates/4e195a7134d8}{Certificate Link}
\end{itemize}

\end{document}